Soundness Proof of Dynamic Shortcut

### 2020-11-23 paper/pldi21/report/def.tex
Almost complete termination proof

We define a $\atriage$ function using two converters between analysis elements
as follows:
\begin{definition}[$\atriage$]\label{def:atriage}
  The triage function $\atriage: \aelemset \rightarrow \aelemset$ for analysis
  elements is defined as
  \[
    \atriage(\aelem) = \left\{
      \begin{array}{ll}
        \asconverter(\aelem)
        & \text{if} \; \aelem = (\view, \abselem) \wedge \aelem \in
        \Dom(\asconverter)\\
        \saconverter(\aelem)
        & \text{if} \; \aelem = (\absimap, \symbst) \wedge \symbst \symbtrans
        \bot\\
        \aelem
        & \text{Otherwise}
      \end{array}
    \right.
  \]
\end{definition}
Using the $\atriage$ function for analysis elements, we defined the $\triage$
function for combined states:
\begin{definition}[$\triage$]\label{def:triage}
  The triage function $\triage: \combdom \rightarrow \combdom$ for combined
  states is defined as
  \[
    \triage((\sabselem, \symbelem)) = \left(
      \lambda \view. \bigjoin \{ \abselem \!\mid\! (\view, \abselem) \in E \},
      E \cap (\absimapset \times \symbstset)
    \right)
  \]
  where
  \[
    E = \dot{\atriage}(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \} \cup \symbelem)
  \]
\end{definition}
The dot notation $\dot{f}$ denotes the element-wise extended function of a
function $f$.

\begin{definition}[Combined One-Step Execution]
  We define the combined one-step execution $\combstep: \combdom \rightarrow
  \combdom$ is define as follows:
  \[
    \combstep(\combelem) = (
      \sabsstep(\sabselem),
      \symbstep(\symbelem)
    )
  \]
  where $(\sabselem, \symbelem) = \triage(\combelem)$.
\end{definition}

>>>>

We define a $\areform$ function using two converters between analysis elements
as follows:
\begin{definition}[$\areform$]\label{def:areform}
  The reform function $\areform: \aelemset \rightarrow \aelemset$ for analysis
  elements is defined as
  \[
    \areform(\aelem) = \left\{
      \begin{array}{ll}
        \asconverter(\aelem)
        & \text{if} \; \aelem = (\view, \abselem) \wedge \aelem \in
        \Dom(\asconverter)\\
        \saconverter(\aelem)
        & \text{if} \; \aelem = (\absimap, \symbst) \wedge \symbst \symbtrans
        \bot\\
        \aelem
        & \text{Otherwise}
      \end{array}
    \right.
  \]
\end{definition}
Using the $\areform$ function for analysis elements, we defined the $\reform$
function for combined states:
\begin{definition}[$\reform$]\label{def:reform}
  The reform function $\reform: \combdom \rightarrow \combdom$ for combined
  states is defined as
  \[
    \reform((\sabselem, \symbelem)) = \left(
      \lambda \view. \bigjoin \{ \abselem \!\mid\! (\view, \abselem) \in E \},
      E \cap (\absimapset \times \symbstset)
    \right)
  \]
  where
  \[
    E = \dot{\areform}(\{ (\view, \sabselem(\view)) \mid \view \in \viewset \} \cup \symbelem)
  \]
\end{definition}
The dot notation $\dot{f}$ denotes the element-wise extended function of a
function $f$.

\begin{definition}[Combined One-Step Execution]
  We define the combined one-step execution $\combstep: \combdom \rightarrow
  \combdom$ is define as follows:
  \[
    \combstep(\combelem) = (
      \sabsstep(\sabselem),
      \symbstep(\symbelem)
    )
  \]
  where $(\sabselem, \symbelem) = \reform(\combelem)$.
\end{definition}
